Title

### 2024-06-25 paper/main.tex
Updates

Many questions in science center around a causal understanding between
variables. \emph{Causal Discovery} aims to find the underlying causal structure
among random variables from a given dataset. The problem of causal discovery
has been studied both in Directed Acyclic Graphs (DAGs) and Structural Equation
Models (SEM) literatures. In the DAG literature, the focus has been on
developing automated algorithms that can learn the causal structure from a
given observational or interventional dataset, whereas in the SEM literature
the focus has on developing tools to help researchers construct or modify
manually constructed models.

@@

In the DAG literature, many automated algorithms have been developed for causal
discovery such as constraint based method (PC, FCI), score-based methods
(Hill-Climb Search, Greedy Equivalence Search), and optimization based methods.
However, the adaption of these algorithms in applied fields remain limited. In
these applied fields, researchers typically prefer to construct these DAGs
manually based on their domain knowledge. We hypothesize that this preference
towards manual DAG construction stems from the following difficulties in
applying causal discovery methods:

>>>>

Many questions in science center around understanding the cause and effect
relationships between variables, as it can reveal the underlying mechanisms for
the observed phenomena and inform effective interventions or policy decisions.
\emph{Causal Discovery} methods aim to find the underlying causal structure
among random variables from a given dataset. The problem of causal discovery
has been studied in both Directed Acyclic Graphs (DAGs) and Structural Equation
Models (SEM) literatures with different approaches. In the DAG literature, the
focus has been on developing automated algorithms that can learn the causal
structure from a given observational or interventional dataset, whereas in the
SEM literature the focus has on developing tools to help researchers construct 
models manually or modify manually constructed models.

@@

In the DAG literature, many automated algorithms have been developed for causal
discovery such as constraint based methods like PC \citep{Spirtes2001} and FCI
\citep{Spirtes2000}, score-based methods like Hill-Climb Search, Greedy
Equivalence Search \citep{Chickering2002}, and optimization based methods.
However, the adaption of these algorithms in applied fields remain limited
\citep{Tennant2020}. In applied fields, researchers typically prefer to
construct these DAGs manually based on their domain knowledge. We hypothesize
that this preference towards manual DAG construction stems from the following
difficulties in applying causal discovery methods:
